Justification for Employing Support Vector Detector in Large-Scale MIMO Systems

### 2015-11-27 Report Nov 2015/Report Nov 2015.tex
Report Nov 2015

%\documentclass[journal]{IEEEtran}
\documentclass[12pt, draftclsnofoot, onecolumn]{IEEEtran}
%\documentclass[12pt,paper,final]{article}
%
%\documentclass[12pt, onecolummn]{report}
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[journal]{../sty/IEEEtran}

@@

\begin{document}
\begin{spacing}{2}
%\doublespacing
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Report: Complex Support Vector Detector for Large MIMO System}

%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%
\author{Tianpei Chen\\
Department of Electrical and Computer Engineering\\
McGill University\\
\today}

@@

@@

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
%\begin{abstract}
%The abstract goes here.
%\end{abstract}

% Note that keywords are not normally used for peerreview papers.
%\begin{IEEEkeywords}
%IEEEtran, journal, \LaTeX, paper, template.
%\end{IEEEkeywords}

% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

\section{Introduction}
% The very first letter is a 2 line initial drop letter followed
% by the rest of the first word in caps.
% 
% form to use if the first word consists of a single letter:
% \IEEEPARstart{A}{demo} file is ....
% 
% form to use if you need the single drop letter followed by
% normal text (unknown if ever used by IEEE):
% \IEEEPARstart{A}{}demo file is ....
% 
% Some journals put the first two words in caps:
% \IEEEPARstart{T}{his demo} file is ....
% 
% Here we have the typical use of a "T" for an initial drop letter
% and "HIS" in caps to complete the first word.
%\IEEEPARstart{T}{his} demo file is intended to serve as a ``starter file''
%for IEEE journal papers produced under \LaTeX\ using
%IEEEtran.cls version 1.8a and later.
% You must have at least 2 lines in the paragraph with the drop letter
% (should never be an issue)
%I wish you the best of success.

@@

%\hfill September 17, 2014
  One of the biggest challenges the researchers and industry practitioners are facing in wireless communication area is how to bridge the sharp gap between increasing demand of high speed communication of rich multimedia information with high level Quality of Service (QoS) requirements and the limited radio frequency spectrum over a complex space-time varying environment. The promising technology for solving this problem, Multiple Input Multiple Output (MIMO) technology has been of immense research interest over the last several tens of years is incorporated into the emerging wireless broadband standard like 802.11ac\cite{IEEE802.11ac} and long-term evolution (LTE)\cite{3GLTE}.  The core idea of MIMO system is to use multiple antennas at both transmitting and receiving end, so that multiplexing gain (multiple parallel spatial data pipelines that can improve spectrum efficiency) and diversity gain (better reliability of communication link) are obtained by exploiting the spatial domain. Large MIMO (also called Massive MIMO) is an upgraded version of conventional MIMO technology employing hundreds of low power low price antennas at base station (BS), that serves several tens of terminals simultaneously. This technology can achieve full potential of conventional MIMO system while providing additional power efficiency as well as system robustness to both unintended man-made interference and intentional jamming.\cite{rusek2013scaling}\cite{larsson2014massive}.

  The price paid for large MIMO system is the increased complexities for signal processing at both transmitting and receiving ends. The uplink detector is one of the key components in a large MIMO system. With orders magnitude more antennas at the BS, benefits and challenges coexist in designing of detection algorithms for the uplink communication of large MIMO systems. On one hand, a large number of receive antennas provide potential of large diversity gains, on the other hand, complexities of the algorithms become crucial to make the system practical.

Vertical Bell Laboratories Layered Space-Time (V-BLAST) architecture for MIMO system can achieve high spectrum efficiency by spatial multiplexing (SM), that is, each transmit antenna transmits independent symbol streams. However the optimal maximum likelihood detector (MLD) for V-BLAST systems that perform exhaustive search has a complexity that increases exponentially with the number of transmitted antennas, which is prohibitive for practical applications.

As alternatives to MLD, linear detectors (LD) such as zero-forcing (ZF) and minimum mean square error (MMSE) with optimized ordering sequential interference cancellation (ZF-OSIC, MMSE-OSIC) are exploited in V-BLAST architecture\cite{wolniansky1998v}\cite{foschini1999simplified}\cite{benesty2003fast},  however the performance of ZF-OSIC and MMMSE-OSIC are inferior comparing to MLD.

Sphere Decoder (SD)\cite{damen2003maximum} is the most prominent algorithm that utilizes the lattice structure of MIMO systems, which can achieve optimal performance with relatively much lower complexity comparing to MLD. However, SD has two major shortages that make it problematic to be integrated into a practical systems. The first shortage is SD has various complexities under different signal to noise ratios (SNR), while a constant processing data rate is required for hardware. The second shortage is the complexity of SD still has a lower bound that increases exponentially with the number of transmit antennas and the order of modulation scheme\cite{jalden2005complexity}.
The fixed complexity sphere decoder (FCSD)\cite{barbero2008fixing} makes it possible to achieve near optimal performance with a fixed complexity under different values of SNR. The FCSD inherits the principle of list based searching algorithms, which first generate a list of candidate symbol vectors and then the best candidate is chosen as the solution. The other sub optimal detectors belong to this class include Generalized Parallel Interference Cancellation (GPIC)\cite{luo2008generalized} and Selection based MMSE-OSIC (sel-MMSE-OSIC)\cite{radji2009interference}. However, all these list based searching algorithms have the same shortage - their complexities increase exponentially with the number of transmit antennas and the order of modulation scheme\cite{radji2009interference}. Therefore, such algorithms are prohibitive when it comes to a large number of antennas or a high order modulation scheme, for example in IEEE 802.11ac standard\cite{IEEE802.11ac}, the modulation scheme is 256QAM.

%Linear detectors (LD) like minimum mean square error (MMSE) and zero forcing (ZF) along with their sequential interference cancellation with optimized ordering (OSIC) counterparts\cite{wolniansky1998v}, which have good performance for low loading factor in massive MIMO system (the number of receive antennas is much larger than the number of transmit antennas)\cite{hoydis2013massive}. 
Besides the above detection algorithms designed for conventional MIMO systems, in the last several years, a set of metaheuristic based detection algorithms have been proposed for large MIMO systems with complexities that are comparable with MMSE detector and near-optimal performance. such algorithms include likelihood ascend searching (LAS) algorithms\cite{vardhan2008low}\cite{li2010multiple}, %An theoretical analysis of upper bound of bit error rate (BER) and lower bound of on asymptotic multiuser efficiency for the LAS detector was also presented\cite{sunfamily}.
Tabu search based algorithms which have superior performances compared to LAS detectors because of the efficient local minima exit strategy (e.g. Layered Tabu search (LTS)\cite{srinidhi2011layered}, Random Restart Reactive Tabu search (R3TS)\cite{datta2010random}), Message passing technique based algorithms (e.g. Belief propagation (BP) detectors based on graphic model and Gaussian Approximation (GA)\cite{som2011low}\cite{som2010improved}\cite{narasimhan2014channel}\cite{goldberger2011mimo}), Probabilistic Data Association based algorithms \cite{mohammed2009low}, Monte Carlo sampling based algorithms (e.g. Markov Chain Monte Carlo (MCMC) algorithm\cite{datta2013novel}) . Moreover, element based Lattice Reduction (LR) aided algorithms were also proposed to  large MIMO systems.\cite{zhou2013element}.

Firmly grounded in framework of statistical learning theory, the Support Vector Machine (SVM) technique has become a powerful tool to solve real world supervised learning problems such as classification, regression and prediction. the SVM method is a nonlinear generalization of Generalized Portrait algorithm developed by Vapnik in 1960s\cite{vapnik1963pattern}\cite{vapnik1964note}, which can provide good generalization performance\cite{scholkopf2002learning}.

Interest in SVM boosted since 1990s, promoted by the works of Vapnik and co-workers at AT\& T Bell laboratory\cite{boser1992training}\cite{guyon1993automatic}\cite{vapnik2013nature}\cite{cortes1995support}\cite{scholkopf1996incorporating}\cite{vapnik1996support}.
Moreover, the kernel based methods\cite{scholkopf2002learning} were proposed which solve nonlinear learning tasks by mapping input data samples into high dimensional feature spaces, and replacing inner products of feature mappings by computational inexpensive kernel functions discarding the actual structure of the feature space. This rationale is supported mathematically by the notion of Reproducing Kernel Hilbert Space (RKHS). 
Based on the same regularized risk function principle, $\epsilon$-Support Vector Regression ($\epsilon$-SVR) was developed\cite{vapnik2013nature}\cite{smola2004tutorial}.

Similar to SVM, the $\epsilon$-SVR solves an original optimization problem by transforming it into a Lagrange dual form, which can be solved by Quadratic Programming (QP). Decomposition methods were proposed to solve this QP problem by decomposing it into sub QP problems and solving them iteratively\cite{platt1999fast}. Therefore, the computational intensive numerical methods can be avoided. Decomposition is performed by sub set selection solver, which refers to a set of algorithms that separate the optimization variables (Lagrange multipliers) into two sets S and N, S is the work set and N contains the remaining optimization variables. In each iteration, only the optimization variables in the work set is updated while keeping other optimization variables fixed. The Sequential Minimal Optimization (SMO) algorithm\cite{platt1999fast} is an extreme case of the decomposition solvers. An important issue of the sub set selection solvers is the selection of the work set. One strategy is to choose Karush-Kuhn-Tucker (KKT) condition violators, ensuring the final converge\cite{osuna1997improved}. The SMO algorithm restricts the size of the work set to two. A method to train SVM without offset was proposed In\cite{steinwart2011training}, with the comparable performance to the SVM with offset. A set of sequential single variable work set selection strategies, which require $O(n)$ searching time are proposed. The optimal double variable work set selection strategy, which performs exhaustively searching, however, requires $O(n^{2})$ searching time. The authors demonstrate that with the combination of two different proposed single variable work set selection strategies, convergence can be achieved by a iteration time that is as few as optimal double variable work set selection strategy.

The mathematical foundation of kernel based methods is RKHS which is defined in complex domain, however most of the practitioners are dealing with real data sets. In communication and signal processing area, the channel gains, signals, waveforms etc. are all represented in complex form. Recently, a pure complex SVR \& SVM based on complex kernel was proposed in\cite{bouboulis2013complex}, which can deal with the complex data set purely in complex domain. The results in\cite{bouboulis2013complex} demonstrate the better performance as well as reduced complexity comparing to simply split learning task into two real case by real kernels.  
Based on this work, we derive a complexity-performance controllable detector for large MIMO systems based on a dual channel complex SVR (CSVR). The detector can work in two parallel real SVR channels which can be solved independently. Moreover, only the real part of kernel matrix is needed in both channels. This means a large amount of computation cost saving can be achieved.
Based on the discrete time MIMO channel model, in our regression model, this CSVR-detector
is constructed without offset, Therefore, for each real SVR without offset, 
%in principle, only one variable is needed to be updated in each iteration, In our scheme, a sequential single variable selection strategy is proposed. By this strategy, two variables can be updated at each iteration, with much smaller searching time.
Two types of combined single optimization variable selection strategy are proposed based on the work in \cite{steinwart2011training}. The proposed combined single optimization variable selection strategy can approximate optimal double optimization variable selection strategy. The former one can achieve as few as iteration time while enjoy significant speed gain in each iteration.

%\subsection{Subsection Heading Here}
%Subsection text here.

@@

%\subsubsection{Subsubsection Heading Here}
%Subsubsection text here.

\section{Brief Introduction to $\epsilon$-Support Vector Regression}\label{Introduce epsilon SVR}
\subsection{Regression Model}
Suppose we are given a training data set $((\mathbf{x}_{1}, y_{1}),(\mathbf{x}_{2},y_{2}),\cdots,(\mathbf{x}_{L},y_{L}))$, $L$ denotes the number of training samples, $\mathbf{x}_{i}\in \mathbb{R}^{V}$ denotes input data vector, $V$ is the number of features in $\mathbf{x}_{i}$. $y_{i}$ denotes output. Let $\mathbf{w}$ denotes regression coefficient vector, $\Phi(\mathbf{x}_{i})$ denotes the mapping of $\mathbf{x}_{i}$ to higher dimensional feature space, $\mathbf{w},\Phi(\mathbf{x}_{i})\in \mathbb{R}^{\Omega}$, $\Omega \in \mathbb{R}$ denotes the dimension of mapped feature space (For linear model, $\mathbf{x}_{i}=\Phi(\mathbf{x}_{i})$, $\Omega=V$). The regression model (either linear or non-linear) is given by 
\begin{equation}
y_{i}=\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b  \quad i= 1,2,\ldots, L
\label{equation1}
\end{equation}

\begin{figure}
\centering
\def\svgwidth{\columnwidth}
\input{epsilon-SVR.pdf_tex}
\caption{$\epsilon$-Support Vector Regression and Risk Functional}
\label{epsilon-SVR}
\end{figure}

We present the primal optimization problem directly
\begin{IEEEeqnarray}[\relax]{l}
\nonumber
\min_{\mathbf{w}} f(\mathbf{w})=\frac{1}{2}||\mathbf{w}||^{2}+C\sum_{i=1}^{L}(R(\xi_{i})+R(\hat{\xi}_{i}))\\
s.t. \left\{\begin{array}{ll}
y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})-b \leq \epsilon+\xi_{i}, i=1,2\cdots, L \\
\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-y_{i} \leq \epsilon+\hat{\xi}_{i}, i=1,2\cdots, L\\
\epsilon_{i}, \xi_{i},\hat{\xi}_{i} \geq 0, i=1,2\cdots, L
\end{array}\right.
\label{primal optimization problem}
\end{IEEEeqnarray}
In (\ref{primal optimization problem}), $\frac{1}{2}||\mathbf{w}||^{2}$ is the regularization term in order to ensure the flatness of regression model, $\epsilon$ denotes the precision, As shown in Fig \ref{epsilon-SVR}, the solid line represents the estimation of the input-output relation, the area between two dash lines ($\epsilon$-bound) is called $\epsilon$-tube. Only those data samples located outside $\epsilon$-tube contribute to the estimation error. Furthermore $\xi_{i}$ and $\hat{\xi}_{i}$ denote slack variables that cope with additive noise of observations, $R(u)$ denotes the cost function. The simplest cost function is $R(u)=u$, The type of cost function is determined by the statistical distribution of noise\cite{smola2004tutorial}. For example if the noise is Gaussian distributed, then the optimal cost function is $R(u)=\frac{1}{2}u^{2}$. The term $C\sum_{i=1}^{L}(R(\xi_{i})+R(\hat{\xi}_{i}))$ denotes the penalty of noise, $C\in \mathbb{R}$ and $C\geq 0$ that controls the trade off between regularization term and cost function term.

In $\epsilon$-SVR, the objective to exploit slack variables $\xi_{i}$ and $\hat{\xi}_{i}$ is to compensate the influences from the outliers that exceed the $\epsilon$-tube which are caused by noise.
Therefore in $\epsilon$-SVR, $\xi_{i}$ and $\hat{\xi}_{i}$ are defined as  
\begin{IEEEeqnarray}[\relax]{l}
\label{definition of slack variable1}
\xi_{i}=\max(0, y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})-b-\epsilon)\\
\label{definition of slack variable2}
\hat{\xi}_{i}=\max(0, \mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-y_{i}-\epsilon).
\end{IEEEeqnarray} 
Because the distance between the estimations $\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b$ and the observation $\mathbf{y}_{i}$ can only exceeds the $\epsilon$-tube in one direction, therefore there is at most one of $\xi_{i}$ and $\hat{\xi}_{i}$ can be non zero. That is $\xi_{i}\hat{\xi}_{i}=0$.
\subsection{Cost Function}\label{cost function}
The optimal cost function in (\ref{primal optimization problem}) can be derived based on maximum likelihood (ML) principle. Assume the data samples $\mathbf{x}_{i}$ in data set are iid, Let $f_{true}(\mathbf{x}_{i}), i=1,2,\cdots L$ denotes true regression function. the underlying assumption is $y_{i}=f_{true}(\mathbf{x}_{i})+\xi_{i}, i=1,2,\cdots, L$, $\xi_{i}$ denotes additive noise of the $i$th data sample, with probability density function (pdf) $Pr(\cdot)$. Let $P(\cdot)$ denotes the pdf of $y_{i}$. Based on ML principle we want to 
\begin{IEEEeqnarray}[\relax]{l}
\nonumber
\max_{f}\quad \prod_{i=1}^{L}P(y_{i}|f(\mathbf{x}_{i}))=\prod_{i=1}^{L}P(f(\mathbf{x}_{i})+\xi_{i}|f(\mathbf{x}_{i}))=\prod_{i=1}^{L}Pr(\xi_{i})=\prod_{i=1}^{L}Pr(y_{i}-f(\mathbf{x}_{i}))\\
\label{cost function1}
\end{IEEEeqnarray}
Take the logarithm of $\prod_{i=1}^{L}Pr(y_{i}-f(\mathbf{x}_{i}))$, we have
\begin{IEEEeqnarray}[\relax]{l}
\sum_{i=1}^{L}\log(Pr(y_{i}-f(\mathbf{x}_{i}))),
\label{cost function2}
\end{IEEEeqnarray}

>>>>

%\documentclass[journal]{IEEEtran}
\documentclass[10pt, draftclsnofoot, onecolumn]{IEEEtran}
%\documentclass[12pt,paper,final]{article}
%
%\documentclass[12pt, onecolummn]{report}
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[journal]{../sty/IEEEtran}

@@

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Justification for Employing Support Vector Detector in Large-Scale MIMO Systems}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%

@@

\author{Tianpei Chen\\
Department of Electrical and Computer Engineering\\
McGill University, Montreal, Quebec, Canada\\
\today}

@@

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
This report provides the justifications for employing support vector regression (SVR) in the detection problem of Large-Scale MIMO (LS-MIMO) systems, which have medium or full loading factor (number of transmit antennas is close or equal to the number of receive antennas). Under this condition, LS-MIMO detection in the view of statistical learning is a multidimensional linear regression problem, given a small training data set. We compare linear detectors (LD) (zero forcing (ZF) and minimum mean square error (MMSE)) with SVR in view of statistical learning theory and demonstrate the better performance that SVR possess over LD in the high spectrum efficiency LS-MIMO systems with medium and full loading factor.
\end{abstract}

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
Large-Scale MIMO, full loading, statistical learning theory, support vector regression, linear detectors
\end{IEEEkeywords}

% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
%\IEEEpeerreviewmaketitle

\section{Large-Scale MIMO System Model and Equivalent Regression Estimation Problem}
% The very first letter is a 2 line initial drop letter followed
% by the rest of the first word in caps.
% 
% form to use if the first word consists of a single letter:
% \IEEEPARstart{A}{demo} file is ....
% 
% form to use if you need the single drop letter followed by
% normal text (unknown if ever used by IEEE):
% \IEEEPARstart{A}{}demo file is ....
% 
% Some journals put the first two words in caps:
% \IEEEPARstart{T}{his demo} file is ....
% 
% Here we have the typical use of a "T" for an initial drop letter
% and "HIS" in caps to complete the first word.
%\IEEEPARstart{T}{his} demo file is intended to serve as a ``starter file''
%for IEEE journal papers produced under \LaTeX\ using
%IEEEtran.cls version 1.8a and later.
% You must have at least 2 lines in the paragraph with the drop letter
% (should never be an issue)
%I wish you the best of success.

@@

%\hfill September 17, 2014
In this section, we present the system model of Large-Scale MIMO (LS-MIMO) systems and the equivalent regression estimation model in view of statistical learning.

\subsection{System Model}
Consider a uncoded complex LS-MIMO uplink spatial multiplexing (SM) system, uplink means the data streams are transmitted from users to base stations (BS). Let $N_{t}$ denotes the number of transmit antennas and $N_{r}$ denotes the number of receive antennas, $N_{r}\geq N_{t}$, define loading factor $\alpha=\frac{N_{t}}{N_{r}}$. Typically LS-MIMO systems have hundreds of receive antennas at BS.

Independent bit sequences, which are modulated to complex symbols are transmitted over flat and slow fading channel. The discrete time model of LS-MIMO systems in the complex domain is given by 
\begin{equation}
\mathbf{y}_{c}=\mathbf{H}_{c}\mathbf{s}_{c}+\mathbf{n}_{c},
\label{complex MIMO model}
\end{equation}
where $\mathbf{y}_{c}\in \mathbb{C}^{N_{r}\times 1}$ denotes the receive symbol vector, $\mathbf{H}_{c}\in \mathbb{C}^{N_{r}\times N_{t}}$ denotes the Rayleigh fading propagation channel matrix. Each component of $\mathbf{H}_{c}$ is independent identically distributed (i.i.d), circularly symmetric complex Gaussian (CSCG) random variables with zero mean and unit variance. $\mathbf{s}_{c}\in \mathbb{C}^{N_{t}\times 1}$ denotes the transmit symbol vector. Each transmit symbol is equally probable and mutually independent, taken from a finite signal constellation alphabet $\mathbb{O}$ (4-QAM, 16-QAM and 64-QAM), $|\mathbb{O}|=M$. $\mathbf{s}_{c}\in \mathbb{O}^{N_{t}}$, satisfies $\mathbb{E}(\mathbf{s}_{c}\mathbf{s}^{H}_{c})=\xi_{s}\mathbf{I}_{N_{t}}$, where $\mathbb{E}(\cdot)$ denotes expectation operator, $(\cdot)^{H}$ denotes Hermitian transpose, $\xi_{s}$ denotes the average power of each component in $\mathbf{s}_{c}$, $\mathbf{I}_{N_{t}}\in \mathbb{C}^{N_{t}\times N_{t}}$ is an identity matrix. $\mathbf{n}_{c}\in \mathbb{C}^{N_{t}\times 1}$ denotes i.i.d additive white Gaussian noise with zeros mean and satisfies $\mathbb{E}(\mathbf{n}_{c}\mathbf{n}^{H}_{c})=N_{0}\mathbf{I}_{N_{r}}$. $N_{0}$ denotes the power spectrum density of each component in $\mathbf{n}_{c}$. The signal to noise ratio (SNR) is defined as $\frac{\xi_{s}}{N_{0}}$.

The discrete time model in (\ref{complex MIMO model}) is defined in complex domain, one can transfer this model into an equivalent real-valued model. Let $\Re(\cdot)$ denotes the real part and $\Im(\cdot)$ denotes the imaginary part, $\mathbf{y}_{c}, \mathbf{H}_{c}, \mathbf{s}_{c}$ and $\mathbf{n}_{c}$ can be decomposed by

\newcommand{\mysmallarraydecl}{\renewcommand{%
\IEEEeqnarraymathstyle}{\scriptscriptstyle}%
\renewcommand{\IEEEeqnarraytextstyle}{\scriptsize}%
\renewcommand{\baselinestretch}{1.1}%
\settowidth{\normalbaselineskip}{\scriptsize
\hspace{\baselinestretch\baselineskip}}%
\setlength{\baselineskip}{\normalbaselineskip}%
\setlength{\jot}{0.25\normalbaselineskip}%
\setlength{\arraycolsep}{2pt}}

\begin{IEEEeqnarray}[\relax]{l}
\nonumber
\mathbf{y}_{c}=\Re{(\mathbf{y}_c)}+\jmath \Im{(\mathbf{y}_{c})}, \mathbf{H}_{c}=\Re{(\mathbf{H}_{c})}+\jmath \Im{(\mathbf{H}_{c})},\\
\mathbf{s}_{c}=\Re{(\mathbf{s}_{c})}+\jmath \Im{(\mathbf{s}_{c})}, \mathbf{n}_{c}=\Re{(\mathbf{n}_{c})}+\jmath \Im{(\mathbf{n}_{c})},
\label{complex decomposition}
\end{IEEEeqnarray}
define

\begin{IEEEeqnarray}[\relax]{l}
\nonumber
\mathbf{y}=[\Re{(\mathbf{y}_{c})}^{T}, \Im{(\mathbf{y}_{c})}^{T}]^{T}, \mathbf{H}=\left[\begin{IEEEeqnarraybox*}[\mysmallarraydecl][c]{,c/c,}
\Re{(\mathbf{H}_{c})}& -\Im{(\mathbf{H}_{c})}\\
\Im{(\mathbf{H}_{c})}& \Re{(\mathbf{H}_{c})}
\end{IEEEeqnarraybox*}\right] \\
\mathbf{s}=[\Re{(\mathbf{s}_{c})}^{T}, \Im{(\mathbf{s}_{c})}^{T}]^{T}, \mathbf{n}=[\Re{(\mathbf{n}_{c})}^{T}, \Im{(\mathbf{n}_{c})}^{T}]^{T},
\label{real vectors}
\end{IEEEeqnarray}
The complex model in (\ref{complex MIMO model}) can be transferred into an equivalent real-valued model, which is given by 
\begin{equation}
\mathbf{y}=\mathbf{H}\mathbf{s}+\mathbf{n},
\label{real MIMO model}
\end{equation}
\subsection{MIMO Detection in view of Statistical Learning}
Generally speaking, the task of LS-MIMO detection is to estimate the transmit symbol vector $\mathbf{s}$ based on the knowledge of receive symbol vector $\mathbf{y}$ and channel state information (CSI) $\mathbf{H}$. In view of statistical learning, LS-MIMO detection problem is a multidimensional ($N_{t}$) regression estimation problem with $N_{r}$ training data samples, which is given by 
\begin{equation}
\mathbf{y}_{i}=f_{LS-MIMO}(\mathbf{h}_{i})+\mathbf{n}_{i}, i=1,2,\ldots, N_{r},
\label{multidimensional regression estimation}
\end{equation}
where $\mathbf{h}_{i}$ denotes the $i$th row of $\mathbf{H}$, is the $i$th input data vector, $f_{LS-MIMO}(\mathbf{h}_{i})=\mathbf{h}_{i}\mathbf{s}$, is a $N_{t}$-dimensional linear function, $\mathbf{s}$ is the regression coefficient vector, $\mathbf{y}_{i}$ is the $i$th observation disrupted by additive noise (error) $\mathbf{n}_{i}$.

The loss function $L(\mathbf{y}_{i}, f_{c}(\mathbf{h}_{i}))$ is a measure of the loss between the observations and the output of a candidate function $f_{c}{\cdot}$, the actual risk of a regression estimate $f_{c}(\cdot)$ is defined by\cite{vapnik1998statistical}
\begin{equation}
R(f_{c})=\int L(y, f_{c}(h))dP(y, \mathbf{h}), f_{c}\in \Lambda
\label{actual risk}
\end{equation} 
where $\Lambda$ is the set of candidate functions, $P(y, \mathbf{h})$ is the joint probability density function (pdf) of input-output data set $(y, \mathbf{h})$ where $y$ is a real value and $\mathbf{h}$ is a vector, (\ref{actual risk}) is the expectation of loss function. The goal of regression estimation is to find the best function $f_{0}(\cdot)$ (e.g., the most accurate approximation to the regression coefficient vector $\mathbf{s}$ in (\ref{multidimensional regression estimation})) that minimize the actual risk, based on the training data set.

The loss function for regression estimation, based on Huber's robust estimator principle\cite{huber2011robust} is given by 
\begin{equation}
L(y, f_{c}(\mathbf{h}))=-\ln(Pr(y-f_{c}(\mathbf{h}))),
\label{robust loss function}
\end{equation}  
where $Pr(\cdot)$ denotes the pdf of additive noise, when the additive noise is Gaussian distributed, the robust loss function is given by 
\begin{equation}
L(y, f_{c}(h))=(y-f_{c}(h))^{2},
\label{robust loss function normal}
\end{equation}

@@

\section{Empirical Risk Minimization Principle and Its Correlation with Linear Detectors}
The actual risk is a theoretical measure of the regression estimation performance with respect to all the data set $(y,\mathbf{h})$. However, in practical the training data set is a finite set of the samples in the data set space and the probability measure $P(y,\mathbf{h})$ is unknown, thus empirical risk is used as an alternative measure of the performance of regression estimation performance. Given a training data set $(y_{1}, \mathbf{h}_{1}), (y_{2}, \mathbf{h}_{2}), \ldots, (y_{l}, \mathbf{h}_{l})$, where $l$ is the number of training data, empirical risk is given by 
\begin{equation}
R_{emp}(f_{c})=\frac{1}{l}\sum_{i=1}^{l}L(y_{i}, f_{c}(\mathbf{h}_{i})), f_{c}\in \Lambda
\label{empirical risk}
\end{equation}
For regression estimation problems in LS-MIMO detection, use Huber's robust loss function in (\ref{robust loss function normal}), the empirical risk in LS-MIMO detection is given by 
\begin{equation}
R^{LS-MIMO}_{emp}(f_{c})=\frac{1}{N_{r}}\sum_{i=1}^{N_{r}}(\mathbf{y}_{i}-f_{c}(\mathbf{h}_{i}))^{2},
\label{empirical risk MIMO}
\end{equation}
where $f_{c}(\mathbf{h}_{i})=\mathbf{h}_{i}\hat{\mathbf{s}}$, $\hat{\mathbf{s}}$ is the estimation of the regression coefficient vector. The empirical risk minimization principle (ERM) is to approximate the minimizer $f_{0}$ of actual risk $R(f_{c})$ by the minimizer $f_{emp}$ of the corresponding empirical risk $R_{emp}(f_{c})$.

In MIMO detection, linear detectors (LD) (zeros forcing (ZF) and minimum mean square error (MMSE)) from the view of regression estimation, are the estimators designed based on ERM principle. We elaborate a little further here.

ZF is derived from the principle of solving an unconstrained least square problem in a continuous vector space\cite{kailath2005mimo}, then slicing the results by symbol constellation alphabet (e.g., 4-QAM, 16-QAM or 64-QAM), the unconstrained least square problem is given by 
\begin{equation}
\min_{\hat{\mathbf{s}}}||\mathbf{y}-\mathbf{H}\hat{\mathbf{s}}||^{2}=\min_{\hat{\mathbf{s}}}\sum_{i=1}^{N_{r}}(\mathbf{y}_{i}-\mathbf{h}_{i}\hat{\mathbf{s}})^{2},
\label{ZF least square}
\end{equation}
where $||\cdot||$ denotes 2-norm operator. The solution of (\ref{ZF least square}) is given by 
\begin{equation}
\tilde{\mathbf{s}}=\mathbf{H}^{\dagger}\mathbf{y},
\label{ZF solution}
\end{equation}
where $\mathbf{H}^{\dagger}=(\mathbf{H}^{T}\mathbf{H})^{-1}\mathbf{H}^{T}$ is the pseudo-inverse of $\mathbf{H}$.
